\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{mathpazo}
\renewcommand{\baselinestretch}{1.2}
\usepackage{enumerate}
\usepackage[parfill]{parskip}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{makecell}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}


\graphicspath{ {../images} }
\begin{document}
\input{titlepage}
\tableofcontents
\newpage

\section{What went well?}

\begin{enumerate}
  \item All group members attended every meeting on time and actively reported their work progress to support team cooperation.
  \item When one member encountered a problem and raised it, a flexible meeting was held, and we would work it out together as a team.
  \item Although the project was divided into two groups, front-end and backend, all the group members discussed the details in advance. As a result, the integration process was smooth.
  \item Demo A: We completed all the tasks of sprint 1 listed in the proposal and the demonstration went well. The problems asked by the tutor during the demonstration were explained to his satisfaction.
\end{enumerate}


\section{What did not go well?}

\begin{enumerate}
  \item We did not prepare enough before the start of coding, especially backend.
  \item We did not pay enough attention to documentations, README etc. which caused some redundant work.
  \item Due to limited time, although the front-end and backend had completed integration, there was no time to beautify existing pages.
  \item Backend group members should be more familiar with RestAPI and enhance the python flask application including model usage.
  \item We did not use more data to test the possible bugs in both front-end and backend applications.

\end{enumerate}

\section{Actions to try in the next sprint?}

\begin{center}
\begin{tabular}{ |c|p{10cm}|c| } 
  \hline
  \thead{No.} & \thead{Action} & \thead{Assignee} \\
  \hline
  1 & Write an implementation plan before coding & \makecell{Qinjian Zheng\\Zeyang Zhang\\Huichuan Xu\\Fang Liu\\Jie Yuan}\\
  \hline
  2 & Read and understand relevant documents & \makecell{Qinjian Zheng\\Zeyang Zhang\\Huichuan Xu\\Fang Liu\\Jie Yuan}\\
  \hline
  3 & Set up deadline for integration, leave enough time for fixing bugs and polishing UI &  \makecell{Qinjian Zheng\\Zeyang Zhang\\Huichuan Xu\\Fang Liu\\Jie Yuan}\\
  \hline
  4 & Read documentations and watch tutorials about technology used in backend application & \makecell{Huichuan Xu\\Fang Liu\\Jie Yuan}\\
  \hline
  5 & Put more time in testing & \makecell{Qinjian Zheng\\Zeyang Zhang\\Huichuan Xu\\Fang Liu\\Jie Yuan}\\
  \hline
  \end{tabular}
\end{center}
\newpage
\section{Meeting Details}

Date: 29/06/2022

Time: 2:45pm – 3:45pm

\vspace{1cm}
  \begin{tabular}{ |c|c|c| } 
    \hline
    \thead{Name} & \thead{zID} & \thead{Present} \\
    \hline
    Fang Liu & z5235533 & Y\\
    \hline
    Jie Yuan & z5315183 & Y\\
    \hline
    Huichuan Xu & z5212102 &  Y\\
    \hline
    Zeyang Zhang & z5273456 & Y\\
    \hline
    Qinjian Zheng & z5325742 & Y\\
    \hline
    \end{tabular}
\end{document}